---
title: "NR_5021_project"
authors: "Husain Agha, James Ostille, Clare Gietzel, Hannah Legatzke"
date: "10/3/2018"
output: html_document
---

#Better Know an R Package
##R/Cowplot
Cowplot is a package developed to work in tandem with R/ggplot2. From the cowplot cran page, "The cowplot package is a simple add-on to ggplot2. It is meant to provide a publication-ready theme for ggplot2, one that requires a minimum amount of fiddling with sizes of axis labels, plot backgrounds, etc."


```{r library, message = FALSE}
library(cowplot, tidyverse)
```

###Load in the data
We are using a data set that is within ggplot2 as well as a dataset collected from class responses.

```{r data}
animal <- msleep
#class <-  
```

##ggplot2
First we will make several different plots using solely ggplot2 functions

```{r ggplot}

p <- ggplot(animal, aes(x = order, y = sleep_total)) + theme(axis.text.x = element_text(face = "italic", angle = 90, vjust = 0.5)) + geom_point() + aes(colour = log(bodywt))
p 




```